Theoretical prediction of disrupted Min oscillation in flattened \emph{Escherichia coli}

### 2015-03-16 paper/paper-MinD.tex
eddited stability analysis in paper Tested everything on crystal.

Huang \emph{et al.}~\cite{huang2003dynamic} has performed a linear
stability analysis on a cylindrical model which shows an upper limit
on a steady state solution of a $2\micron$ half wavelength.  Cells
with dimensions longer than this show spontaneous oscillatory behavior
in this direction, while cells that are shorter relax into a
motionless steady state.  We have similarly performed a linear
stability analysis on an infinite slab with a thickness equal to that
of our flattened cells ($0.25\micron$) and have found that an
equivalent stability limit for half wavelength is $2.13\micron$. As
expected, when decreasing the lengths and widths of our simulated
flattened cells so that the longest distance across the cell is less
than this length, the cells stop exhibiting any oscillatory behavior.
The deterministic model relaxes into a motionless state and the
stochastic model exhibits random fluctuations without spatial
oscillations.

>>>>

Huang \emph{et al.}~\cite{huang2003dynamic} has performed a linear
stability analysis on a cylindrical model which shows an upper limit
on a steady state solution of a $2\micron$ half wavelength.  Cells
with dimensions longer than this show spontaneous oscillatory behavior
in this direction, while cells that are shorter relax into a
motionless steady state.  We have similarly performed a linear
stability analysis on an infinite slab with a thickness equal to that
of our flattened cells ($0.40\micron$).  We first solve the model's
five differential equations for the steady state solution, using for
our concentrations of MinD and MinE the same as the total in
simulation.  We then add small, spatially harmonic density
perturbations to the density, throwing away any terms that are
nonlinear in perturbation.  The sign of the eigenvalues of the
resulting matrix informs us whether harmonic perturbations at a
specified wavelength will evolve toward the steady state solution or
not, so picking a wavelength that ensures all eigenvalues are of the
correct sign allows for an upper stability limit. Through this method
we arrive at an upper half wavelength stability limit of $1.56\micron$
for our $0.40\micron$ flattened cells. As expected, when decreasing
the lengths and widths of our simulated flattened cells so that the
longest distance across the cell is less than this length, the cells
stop exhibiting any oscillatory behavior.  The deterministic model
relaxes into a motionless state and the stochastic model exhibits
random fluctuations without spatial oscillations.
